\documentclass[10pt]{article}
    \usepackage[english]{babel}
    \input{config/minimal-resume-config}
    \begin{document}
    
\begin{center}
	% Personal
	% -----------------------------------------------------
	{\fontsize{\sizeone}{\sizeone}\fontspec[Path = fonts/,LetterSpace=15]{Montserrat-Regular} ANAS MOHAMED}
	\\
	\vspace{2mm}
	{\fontsize{0.8em}{0.8em}\fontspec[Path = fonts/]{Montserrat-Light} mail@amohamed.ca -- https://github.com/amohamed11}
\end{center}
% Chapter: Work Experience
% ------------------------
\chap{EXPERIENCE}{
	
	\job
	{Areto Labs}
	{Oct 2021 – Present}
	{Software Developer (Python, Flask, React(Typescript), PostgreSQL, Docker, GCP)}
	{Remote, Canada}
	{\begin{newitemize}
		\item {Led the database design \& greenfield work for a brand new social media sentiment analyzer \& moderator, and worked on expanding support by integrating multiple 3rd party APIs.}
		\item {Was the de-facto full-stack developer, thus worked on every part from the PostgreSQL database, and the Flask/FastAPI backend services to the the React frontend.}
		\item {Contributed to the setting up, evolving, and maintaining of our platform's infrastructure on GCP which included containerized deployments for multiple services.}
		\item {Mentored two interns from on-boarding and familiarzing them with the codebase, to the 1:1 check-ins and continued support.}
		\end{newitemize}}
	\job
	{Eclipse OpenJ9 (Open-Source)}
	{Sept 2020 – Jan 2021}
        {Open Source Contributer (C++)}
	{https://github.com/eclipse/openj9-utils}
	{\begin{newitemize}
                \item {Worked in student team under mentorship of IBM engineers to contirbute to the development of a command-line tool for collecting Eclipse OpenJ9\textquotesingle{}s runtime performance stats utilizing JVMTI for JVM metrics, and perf for system level metrics.}
		\end{newitemize}}
	\job
	{DevFacto}
	{Jan 2019 – Sept 2019}
	{Junior Consultant (C\#, .NET Core, Typescript, React, Azure)}
	{Edmonton, Alberta, Canada}
	{\begin{newitemize}
		\item {Worked on a Geo-mapping web application for managing trailer inventory on construction site. Set up an audit log system, and wrapped up the project for final delivery.}
		\item {Developed and delivered a flexible questionnaire system for commercial use with an easily extensible questionnaire database.}
		\item {Collaborated with UI/UX designers in researching user requirements, stakeholder interview and developing end-user interfaces.}
		\end{newitemize}}
}
% Chapter: Education
% ------------------

\chap{EDUCATION}{
	
	\school
	{University of Alberta}
	{Sep 2016 – Jun 2021}
	{Bachelor of Science with Specialization, Computing Science}
	{Edmonton, Alberta}
	{
	}
}
% Chapter: Skills
% ------------------------

\chap{SKILLS}{
	\begin{newitemize}
		\item Frameworks/Libraries: React, Flask, Ruby on Rails, Django
		\item Programming Languages: Python, Javascript/Typescript, Go
		\item Databases/Cloud Infrastructure: SQLite, PostgreSQL, Heroku, GCP
% 		\item Environments/Tools: Linux, Vim/Neovim, VSCode, Git
	\end{newitemize}
}
% Chapter: Projects
% ------------------------

\chap{PROJECTS}{
	
	\project
	{Kagi}
	{Go}
	{https://github.com/amohamed11/kagi}
	{A lightweight B+Tree-based on-disk key-value store implemented from scratch in Go.\\}
		\project
		{Hogwash}
		{React(Typescript), Ruby on Rails, Heroku}
		{https://github.com/amohamed11/hogwash}
		{A word game based of balderdash but modified for the web. Built with websockets \& fun.\\}
			\project
			{chibiOS}
			{Rust}
			{https://github.com/amohamed11/chibiOS}
			{A small operating system built in Rust, to learn more about systems programming.\\}
	}
\end{document}
